TBD

### 2016-10-06 paper.tex
JHr
added GN and LINCAL section

\newcommand{\bz}{\bmath{z}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\bB}{\bmath{B}}
\newcommand{\bC}{\bmath{C}}
\newcommand{\bE}{\bmath{E}}
\newcommand{\bF}{\bmath{F}}
\newcommand{\bG}{\bmath{G}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bH}{\bmath{H}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\bzero}{\bmath{0}}
\newcommand{\conj}[1]{\overline{#1}}

@@

\begin{equation}
[\bC]_{ij} = 
\begin{cases}
 \sum_{k \neq i} \left | g_k \right |^2 \left | y_{\zeta_{ik}} \right |^2 & \textrm{if} ~ i=j\\
 0 & \textrm{otherwise}
\end{cases},
\end{equation}
\begin{equation}
[\bD]_{ij} = 
\begin{cases}
 g_i y_j^*  \left | g_{\psi_{ij}} \right |^2  & \textrm{if} ~ \psi_{ij}\neq0\\
 0 & \textrm{otherwise}
\end{cases},
\end{equation}

@@

@@

>>>>

\newcommand{\bz}{\bmath{z}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\bB}{\bmath{B}}
\newcommand{\bC}{\bmath{C}}
\newcommand{\bE}{\bmath{E}}
\newcommand{\bF}{\bmath{F}}
\newcommand{\bG}{\bmath{G}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bH}{\bmath{H}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\ba}{\bmath{a}}
\newcommand{\bb}{\bmath{b}}
\newcommand{\bzero}{\bmath{0}}
%\newcommand{\bvarrho}{\bmath{\varrho}}
%\newcommand{\bnu}{\bmath{\nu}}
%\newcommand{\bvarphi}{\bmath{\varphi}}
\newcommand{\conj}[1]{\overline{#1}}

@@

\begin{equation}
[\bC]_{ij} = 
\begin{cases}
 \sum_{k \neq i} \left | g_k \right |^2 \left | y_{\zeta_{ik}} \right |^2 & \textrm{if} ~ i=j\\
 0 & \textrm{otherwise}
\end{cases},
\end{equation}
\begin{equation}
[\bD]_{ij} = 
\begin{cases}
 g_i \conj{y}_j  \left | g_{\psi_{ij}} \right |^2  & \textrm{if} ~ \psi_{ij}\neq0\\
 0 & \textrm{otherwise}
\end{cases},
\end{equation}

@@

Furthermore, substituting Eq.~\eqref{eq:Jacobian_red} into $\bJ^H\breve{\br}$ results in
\begin{equation}
\bJ^H\breve{\br} = \begin{bmatrix}
                   \ba & \bb & \conj{\ba} & \conj{\bb}\\
                   \end{bmatrix}^T,
\end{equation}
where
\begin{align}
\left [ \ba \right ]_i &= \sum_{k\neq i} g_k \widetilde{y}_{ik}r_{ik},  & \left [ \bb \right ]_i &= \sum_{pq\in\mathcal{PQ}_i}\conj{g}_p g_q r_{pq},
\end{align}
and
\begin{equation}
\widetilde{y}_{ik} = 
\begin{cases}
\conj{y}_{\zeta_{ik}} & \textrm{if}~k > i\\
y_{\zeta_{ik}} & \textrm{otherwise}
\end{cases}.
\end{equation}

HAVE TO RECHECK THE ABOVE EQUATIONS DIRECTLY FROM THE CODE.

HAVE TO STATE WHETHER COLUMN OR ROW VECTOR.

% \begin{equation}
% \boldsymbol{J}^H\breve{\boldsymbol{d}} = 
% \begin{bmatrix}
% \sum_{k\neq i } g_k x_{ik}d_{ik}\\
% \sum_{pq \in \mathcal{I}_j} \conj{g}_p g_q d_{pq}\\
% \downarrow^{*}
% \end{bmatrix}
% \begin{matrix}% matrix for right braces 
% \coolrightbrace{\sum g_k x_{\zeta_{ik}}d_{ik}}{i = 1\cdots N}\\
% \coolrightbrace{\sum \conj{g}_p g_q d_{pq}}{j = 1\cdots L}\\
% \vphantom{\downarrow^{*}}
% \end{matrix}
% \end{equation}

@@

STILL NEED TO ADD z k+1 EXPRESSION.

\subsection{GN and LINCAL}
As we mentioned at the start of this section, the Wirtinger framework is not the only way in which we can ensure that $\bv$ is analytic in its argument. We could also 
have divided the problem in Eq ... into its real and imaginary components and then solver for the real and imaginary parts of the parameters separately. There is a third way
of dealing with the issue. We can split the problem in Eq into its phase and amplitude components and then solve for the amplitude and phase of the parameters separately.
This can be achieved by first rewriting Eq. as

\begin{equation}
\label{eq:red_least_squares_lincal}
\min_{\bmath{\varrho}} \|\breve{\br}\| = \min_{\bmath{\varrho}} \|\breve{\bd} - \breve{\bv}(\bmath{\varrho})\|, 
\end{equation}
where $\bmath{\varrho} = \left [\bmath{\eta},\bmath{\varphi},\widetilde{\bmath{\eta}}, \widetilde{\bmath{\varphi}}\right ]^T$. The Jacobian associated with 
Eq.~\eqref{eq:red_least_squares_lincal} is equal to the Eq xxx in the LINCAL section.
We have therefore shown that doing one iteration of LINCAL is equivalent to a basic GN update step; the GN update step was just re-derived in the Appendix from first principles.
An easy why of improving the convergence properties of LINCAL would be to simply add the LM damping factor to the basic LINCAL update step.

\subsection{LM and StEFCal}
